---
title: "AM03_AUT19 Group 10 Group Assignment"
author: "Yifei Yu, Dominic Nadeau, Joséphine De Cuyper, Garima Agarwal"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    toc: yes
    toc_float: yes
---

```{r, setup, include = FALSE}
# Import libraries
library(tidyverse)
```

# Question 1
**a**: "<-" operator is the one I would use for assignment  
**b**: When "=" and "<-" are used in creating an argument for a function, variable created by "<-" will be in the user's workspace while the one created by "==" will not.  
**c**: Variable names must not start with special characters or numbers. Reserved words cannot be used as variable names.  
**d**: Default numeric data type is _double_. 200 is interpreted as a __double__. 
```{r, example for 1d}
typeof(200)
```
**e**: There are numeric, character, integer and logical. Yes because it consists of only atmoic types that cannot be further divided.  

# Question 2
**a**: x < y < z will be evaluated as x < y & y < z  
**b**: "==" is equality. "|" is or. "!=" is inequality. "&" is and. ">" is greatr than.  
**c**: From highest to lowest, ==, !==, >, &, |.  
**d**: TRUE & 5 & FALSE & "abc" & TRUE  
**e**: (5 == 5) | ("abc" != "abc") & (1 > 0)

# Question 3
**a**: 
```{r}
tsla <- c(26150, 29870, 29980, 40740, 83500, 90700, 63000, 95200)
names(tsla) = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7', 'Q8')
print(tsla)
```

**b**
```{r}
n = length(tsla)
tot <- 0
for (i in 1:n){
    tot <- tot + tsla[i]
}
print(tot)
```

**c**: Anything between the bracket after the condition is the codee block while i is the index variable.