---
title: "AM03_AUT19 Group 10 Group Assignment"
author: "Yifei Yu, Dominic Nadeau, Joséphine De Cuyper, Garima Agarwal"
date: "`r Sys.Date()`"
output:
  html_document:
    theme: flatly
    highlight: zenburn
    toc: yes
    toc_float: yes
---

```{r, setup, include = FALSE}
# Import libraries
library(tidyverse)
```

# Question 1
# (a): "<-" the assignment operator 
# (b): When "=" and "<-" are used in creating an argument for a function, variable created by "<-" will be in the user's global environment while the one created by "=" will not. 
# (b): The <- operator has higher precedence over the = operator.
# (c): Variable name can only contain letters, numbers, dots and underscores and should start with a letter or a dot that is not followed by a number. Furthermore, keywords cannot be used as variable names.  
# (d): Default numeric data type is _double_. 200 is interpreted as a __double__. 
```{r, example for 1d}
typeof(200)
```
# (e): The 4 basic data types are: character, numeric, complex and logical. It is correct to say string "I love LBS" is an atomic vector, because it is a character atomic vector of length 1.

# Question 2
# (a): The correct syntax is: x < y & y < z. All relational operators have equal precedence and R interprets the order by applying left to right associativity. 
# (b): "==" is equality check sign (relational operator). "|" is or (logical operator). "!=" is inequality (relational operator). "&" is and (logical operator). ">" is greater than (relational operator).  
# (c): From highest to lowest:
# ==, !==, > (relational operators first)
# &
# | 
# (d): TRUE | FALSE & TRUE
# (e): (5 == 5) | (("abc" != "abc") & (1 > 0))

# Question 3
# (a): 
```{r}
tsla <- c(26150, 29870, 29980, 40740, 83500, 90700, 63000, 95200)
names(tsla) = c('Q1', 'Q2', 'Q3', 'Q4', 'Q5', 'Q6', 'Q7', 'Q8')
print(tsla)
```

# (b): 
```{r}
n = length(tsla)  # variable where you store your data
tot <- 0    # variable where you store your result 
for (i in 1:n){
    tot <- tot + tsla[i]         #code block where [i] is index variable
}
print(tot)
```

# (c): 
# {tot <- tot + tsla[i]} is the code block
# The i in (i in 1:n) is the index variable
